---
title: "R Notebook for False Memory Study Proposal"
output:
  html_notebook:
    toc: true
    toc_float: true
    code_folding: hide
---

# Creating the Datatable

In order to create the datatable we need to define the columns that include information regarding the group which can be control group (control) or experiemental group (subject), subjects can either have positive false memories (FPM) or not have positive false memories (NFPM) implanted to their brains. The independent variable is participants with PTSD who will receive or not recieve the positive false memories. Delayed reward discounting rate is the dependent variable and the discount rates are generated by the normal distribution code that generates 10 numbers around the expected mean determined by the experimenter. 


```{r}
x=1:10
sbj=sprintf("subject %d",x)

cont=sprintf("control %d",x)

subject_withnumber = c(sbj,sbj,cont,cont)
subject = c(rep("subject",20),rep("control",20))
group = c(rep("FPM",10),rep("NFPM",10),rep("FPM",10),rep("NFPM",10))
FPM_subject = rnorm(10,0.15,0.1)
NFPM_subject = rnorm(10,0.88,0.1)
FPM_control = rnorm(10,0.67,0.1)
NFPM_control = rnorm(10,0.15,0.1)
discount_rate = c(FPM_subject,NFPM_subject,
                  FPM_control,NFPM_control)

datatable = data.frame(subject, subject_withnumber, group, discount_rate)
datatable
```
# Bar Plots
```{r}
library(dplyr)
library(ggplot2)
dt2 = datatable %>%
  group_by(group, subject) %>%
  summarise(mean_k = mean(discount_rate),
            sem = sd(discount_rate)/sqrt(n()))

ggplot(dt2, aes(group, mean_k))+
  geom_bar(stat = 'identity')+
  facet_wrap(~subject) +
  geom_errorbar(aes(ymin=mean_k-sem, ymax=mean_k+sem),width=0.4)

datatable %>%
  group_by(group, subject) %>%
  summarise(mean_k = mean(discount_rate), sem=sd(discount_rate/sqrt(n()))) %>%
  mutate(x_axis = paste(group, subject, sep = '_')) %>%
  ggplot(aes(x_axis, mean_k))+
  geom_errorbar(aes(ymin=mean_k-sem, ymax=mean_k+sem),width=0.4) +
  geom_bar(stat = 'identity') +
  xlab("group and subject") + ylab("mean log(k)")
```

# Linear Correlation
```{r}
cor.test(NFPM_subject, FPM_control)
```

```{r}
datatable %>%
  ggplot(aes(group,discount_rate))+
  geom_point()+
  geom_smooth(method="lm") +
  ylab("log(k)")
```

# T-test
```{r}
ggplot(datatable, aes(group, discount_rate))+
  geom_boxplot()+
  facet_wrap(~subject) +
  ylab("log(k)")
```

# ANOVA
```{r}
summary(aov(discount_rate ~ group, datatable))
```
```{r}
datatable %>%
  ggplot(aes(discount_rate, fill=subject, col=subject))+
  geom_density(alpha=0.5) +
  xlab("log(k)")
```

# Linear Regression
```{r}
datatable %>%
  ggplot(aes(discount_rate, group, color=subject))+
  geom_point()+
  geom_smooth(method = "lm") +
  xlab("log(k)")
```

```{r}
summary(lm(discount_rate ~ group+subject, datatable))
```

